Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-16 introduction.tex
Weakened language about galaxy catalog completeness
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1085 ccdd05d5-56c1-461a-bf98-85f6876523b4

It is infeasible to search this large an area for a prompt counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.  However, if we can take galactic luminosities
to accurately trace mass and thus proxy
for the \CBC{} event rate, it is possible to reduce the localization
uncertainty using a galaxy catalog as a prior probability distribution
\citep{galaxy-catalog}, along with the sky location and luminosity distance
estimate from the \GW{} signal, as was done in S6/VSR3. At Advanced \LIGO{}
\textsc{ns}--\textsc{ns} horizon distances of $\sim$400~Mpc, the galaxy catalog
is fairly isotropic and thus not as useful for downselecting pointings, but
sources that are detectable before merger are likely to be exceptionally
nearby. Thus there will be relatively few galaxies to consider for a given
early-warning candidate and the galaxy catalog is likely to be sufficiently
complete. This should allow us to shrink the 90\% confidence area substantially.
Even so, it will be desirable to mobilize a large number of heterogeneous
telescopes in order to guarantee imaging this exceptional event at the instant
of merger. Because the sky localization will improve rapidly until merger,
by the time that the entire \CBC{} event is over it will be
possible to send a second alert to downselect the images that have already been
taken as well as repoint telescopes to more likely locations.

>>>>

It is infeasible to search this large an area for a prompt counterpart. For
reference, \textsc{lsst} should see first light around the same time as
Advanced \LIGO{} and will have an unparalleled field of view of 9.6 deg$^2$
\citep{2008arXiv0805.2366I}.  However, if we can take galactic luminosities
to accurately trace mass and thus proxy
for the \CBC{} event rate, it is possible to reduce the localization
uncertainty using a galaxy catalog as a prior probability distribution
\citep{galaxy-catalog}, along with the sky location and luminosity distance
estimate from the \GW{} signal, as was done in S6/VSR3. At Advanced \LIGO{}
\textsc{ns}--\textsc{ns} horizon distances of $\sim$400~Mpc, the galaxy catalog
is fairly isotropic and thus not as useful for downselecting pointings, but
sources that are detectable before merger are likely to be exceptionally
nearby. Thus there will be fewer galaxies to consider for a given
early-warning candidate and the galaxy catalog is likely to be sufficiently
complete. This should allow us to shrink the 90\% confidence area.
Even so, it will be desirable to mobilize a large number of heterogeneous
telescopes in order to guarantee imaging this exceptional event at the instant
of merger. Because the sky localization will improve rapidly until merger,
by the time that the entire \CBC{} event is over it will be
possible to send a second alert to downselect the images that have already been
taken as well as repoint telescopes to more likely locations.
